Variable Selection

### 2015-06-29 var_select.rmd

>>>>

# New Variable - client age

```{r, echo=FALSE}
#read csv file with all the client details - want to merge this with client df
details<- read.csv('17marchclients.csv',
                   na.strings = c("", " ", "NA"))
head(details)
#delete client.contact, client.count, and contact.count columns
details<- details[,c(1,5:9)]
#rename columns
names(details)[2]<- 'Business'
names(details)[4]<- 'Biz.size'
names(details)[5]<- 'Biz.type'
names(details)[6]<- 'Biz.age'

#delete rows with 4 NA values
details<-details[rowSums(is.na(details))!=5,]
details<-details[rowSums(is.na(details))!=4,]

#add row for client code
code.client<- read.csv('code_client2.csv')[,-1]
details<- merge(details, code.client, by.x ='client', by.y ='client2', all.x=TRUE, all.y=FALSE)
details<- transform(details, client.age = 2014- Biz.age)

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)

See how variable selection goes with random forest first, then probably just run cforest again without code.client and contact.code

Use cforest to test remaining variables (with significant NA components)

These include:

* code.client
* Post.Code
* Billing.Type
* Job.Source
* Job.Detail.Primary
* Job.Detail.Secondary
* Job.Type.Primary
* Job.Type.Secondary
* Type
* Project.Value
* no.employees
* client age????
* contact.count
* JD.Primary
* JD.Second
* dist
* code.contact
* client.age

First eliminate some of the job.detail.secondary - that kind of thing
Then see if any have matching NA rows
Then run cforest on each variable individually
